---
title: "Thesis"
author: "Ann Basting"
output: 
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
#install.packages("Hmisc")
library(Hmisc)
library(corrplot)
#install.packages("e1071")
library(e1071)
library(lmtest)
library(MASS)
#install.packages("plyr")
library(plyr)
library(Metrics)
#install.packages("BMA")
library(BMA)
source("Z:/FluSurv-NET/COVID-19/Ann/Thesis/thesis/analysis/mod_functions.R")
```

## Histogram of scaled covariates


```{r scaled, echo=FALSE}
ggplot(plot_long) +
    geom_histogram(aes(value), bins = 50) +
    facet_wrap(~name, ncol = 4)
  
  hist(scaled$EP_PCI)
  hist(scaled$test.incidence)
```





## Fit of leave in data (predicted vs observed)

```{r leave in, echo=FALSE}
ggplot(fit.check,aes(pred, covidnet.cases ,color = county)) +
      geom_point() +
      geom_abline(slope = 1, color = "red") +
      theme_bw() +
      facet_wrap(~county)
```





## Fit of leave out data (predicted vs observed)

```{r leave out, echo=FALSE}
ggplot(pred.df.rate,aes(predicted.rate, observed.rate, color = county)) +
            geom_point() +
            geom_abline(slope = 1, color = "red") +
            theme_bw() +
            facet_wrap(~county)
```

## coefficients

EP_AGE65   = % of persons 65 and older
EP_DISABL  = % of civilian non-insitutionalized pop with a disability
EP_SNGPNT  = % of single parent households with children under 18 
EP_MINRTY  = % minority
EP_LIMENG  = % of persons (age 5+) who speak English "less than well"
EP_MUNIT   = % of housing in structures with 10 or more units
EP_NOVEH   = % of households with no vehicle available
EP_UNINSUR = % uninsured 
EP_PCI     = per capita income
EP_AGE17   = % of persons aged 17 and younger
EP_MOBILE  = % of mobile homes
EP_UNEMP   = unemployment rate
EP_POV     = % of persons below poverty
EP_NOHSDP  = % of persons with no high school diploma

```{r}
ave.coefs

coefs
```


## linmods

for non-transformed predictor/outcome

```{r non-transformed}
linmod1<-lm(observed.rate~predicted.rate, data = dph.pred)
    summary(linmod1)
   
    plot(linmod1$residuals)
    
    ggplot(dph.pred, aes(x = predicted.rate, y = observed.rate)) + 
      geom_point(alpha = 0.3) +
      stat_smooth(method = "lm", col = "aquamarine3") +
      #geom_abline(slope = 1, linetype = "dotted", size = 1, col = "red")+
      theme_classic()
```


for transformed predictor/outcome

```{r playing with shape of predicted and observed}

hist(log(dph.pred$predicted.rate))
hist(sqrt(dph.pred$observed.rate))

```

```{r transformed}

    linmod2<-lm(log(observed.rate)~log(predicted.rate), data = dph.pred)
    summary(linmod2)
 
    plot(linmod2$residuals)
    
    ggplot(dph.pred, aes(x = log(predicted.rate), y = log(observed.rate))) + 
      geom_point(alpha = 0.3) +
      stat_smooth(method = "lm", col = "aquamarine3") +
      #geom_abline(slope = 1, linetype = "dotted", size = 1, col = "red")+
      theme_classic()
```